Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors

### 2019-01-31 LaTex/Paper_fulltext.tex
Added declaration of authorship

	\section{Introduction and Preliminary remarks}
	Anecdotal evidence suggests that people spend a significant share of their lifetime working (for a casual calculation 
	see: \citet{thompson_what_2016}). Moreover, people's work environment is changing constantly and especially today's 
	discussion about the impact of digitalisation on the labour market requires to investigate how occupational factors shape 
	people's life in general. Since work constitutes a considerable part of people’s life, satisfaction with one’s job and the
	occupational environment must severely determine overall well-being. Drawing on the above-mentioned diversity of 
	occupations, their respective circumstances and adaptation to the ‘digital revolution’, this assumption gains even more 
	ground and relevance: \textit{If work changes, life changes.} \\
	But which work-related factors contribute to a happy - or unhappy - life? Also, how does life satisfaction of the employed
	vary across regions and countries? \\
	Using data form the European Values Study (EVS) and several other sources, we calculated multiple regression models to assess the causality of
	work-related factors and well-being on the individual level. Moreover, multi-level analyses with regard to social capital and
	macroeconomic as well as developmental indicators were performed to account for variation across regions and countries. 
	%% Könntest du den Fokus ein wenig weg von Work und hin auf multilevel + pecuniary/ non-pecuiary setzen, für so viel Fokus haben wir nicht genug work-relatedness
	\section{Motivational Manifesto}
	In a time of widespread digitalisation for many aspects of modern society, 'datafication' and subsequent analysis of data has become ever more prevalent \citep{baack_datafication_2015, lycett_datafication:_2013}. Transparency of data sourcing, data access and methods employed in the course of this analysis is a chief concern of the 'Open Science' movement \citep{delfanti_open_2010}. With more and more transparency, reproducibility of procedures is expected to increase and thus the quality of insights by replication and and improvements of methods through a 'wisdom of the (educated) crowd'. There have been extensive developments in the form of guidelines and protocols for researchers, universities and scientific journals that are aimed at promoting more transparency in the scientific process \citep{nosek_promoting_2015, miguel_promoting_2014}. 
	At the same time, large shares of the population lack the essential skills to participate in the research process or perceive the barrier of entry in acquiring the necessary skills to do so, as insurmountably high. The concept of 'Citizen Science' has thus emerged sitting at the edge of both science and education. Citizen science projects enlist non-scientist members of the public to participate in the research (mainly in data collection), allowing to survey large amounts of data, while educating participants about the research topic \citep{shirk_public_2012}. Originally coming from environmental research this approach has already allowed researcher to survey wide ranges of locations and time periods and thus provides access to high-quality data that could quite impossibly be attained by professional research teams on their own \citep{bonney_citizen_2009}.

	Conceptually, 'Open Science' and 'Citizen Science' are deeply intertwined as 'Citizen Science' needs to be as transparent and easily accessible as possible to be effective on a large scale \citep{nov_dusting_2011} and 'Open Science' needs to offer educational value and low entry barriers if it wants to gain attention and participation of a broader audience \citep{newman_future_2012}. We feel committed to the mission of these movements and have thus designed our project in order to advance it for the social sciences.

@@

\begin{tabular}{|c|c|c|}
	\hline 
	\textbf{Project area}	& \textbf{Noah Peters} 	& \textbf{Nicolas Goeller} 	\\ 
	\hline 
	Data wrangling			&  		   				&  				 			\\ 
	\hline 
	Variable preparation 	&  		   				&  				 			\\ 
	\hline 
	Geodata					&  		   				&  				 			\\ 
	\hline 
	Git	     			 	&  		   				&  				 			\\ 
	\hline 			
	Indices				 	&  		   				&  				 			\\ 
	\hline 
	Paper visualisations 	&  		   				&  				 			\\ 
	\hline 
	Shiny 				 	&  		   				&  				 			\\ 
	\hline 
	Codebook 			 	&  		   				&  				 			\\ 
	\hline 
	Geoplots 			 	&  		   				&  				 			\\ 
	\hline 
	LaTex				 	&  		   				&  				 			\\ 
	\hline 
	Motivation			 	&  		   				&  				 			\\ 
	\hline 
	Theory				 	&  		   				&  				 			\\ 
	\hline 
	User manual			 	&  		   				&  				 			\\ 
	\hline 
\end{tabular}

@@

>>>>

	\section{Introduction and Preliminary remarks}
	Anecdotal evidence suggests that people spend a significant share of their lifetime working (for a casual calculation 
	see: \citet{thompson_what_2016}). Moreover, people's work environment is changing constantly and especially today's 
	discussion about the impact of digitalisation on the labour market requires to investigate how occupational factors shape 
	people's life in general. Since work constitutes a considerable part of people’s life, satisfaction with one’s job and the
	occupational environment must severely determine overall well-being. Drawing on the above-mentioned diversity of 
	occupations, their respective circumstances and adaptation to the ‘digital revolution’, this assumption gains even more 
	ground and relevance: \textit{If work changes, life changes.} \\
	But which work-related factors contribute to a happy - or unhappy - life? Also, how does life satisfaction of the employed
	vary across regions and countries? \\
	Using data form the European Values Study (EVS) and several other sources, we calculated multiple regression models to assess the causality of
	work-related factors and well-being on the individual level. Moreover, multi-level analyses with regard to social capital and
	macroeconomic as well as developmental indicators were performed to account for variation across regions and countries. 
	%% Könntest du den Fokus ein wenig weg von Work und hin auf multilevel + pecuniary/ non-pecuiary setzen, für so viel Fokus haben wir nicht genug work-relatedness
	\section{Motivational Manifesto}
	In a time of widespread digitalisation for many aspects of modern society, 'datafication' and subsequent analysis of data has become ever more prevalent \citep{baack_datafication_2015, lycett_datafication:_2013}. Transparency of data sourcing, data access and methods employed in the course of this analysis is a chief concern of the 'Open Science' movement \citep{delfanti_open_2010}. With more and more transparency, reproducibility of procedures is expected to increase and thus the quality of insights by replication and and improvements of methods through a 'wisdom of the (educated) crowd'. There have been extensive developments in the form of guidelines and protocols for researchers, universities and scientific journals that are aimed at promoting more transparency in the scientific process \citep{nosek_promoting_2015, miguel_promoting_2014}. 
	At the same time, large shares of the population lack the essential skills to participate in the research process or perceive the barrier of entry in acquiring the necessary skills to do so, as insurmountably high. The concept of 'Citizen Science' has thus emerged sitting at the edge of both science and education. Citizen science projects enlist non-scientist members of the public to participate in the research (mainly in data collection), allowing to survey large amounts of data, while educating participants about the research topic \citep{shirk_public_2012}. Originally coming from environmental research this approach has already allowed researcher to survey wide ranges of locations and time periods and thus provides access to high-quality data that could quite impossibly be attained by professional research teams on their own \citep{bonney_citizen_2009}.
	Conceptually, 'Open Science' and 'Citizen Science' are deeply intertwined as 'Citizen Science' needs to be as transparent and easily accessible as possible to be effective on a large scale \citep{nov_dusting_2011} and 'Open Science' needs to offer educational value and low entry barriers if it wants to gain attention and participation of a broader audience \citep{newman_future_2012}. We feel committed to the mission of these movements and have thus designed our project in order to advance it for the social sciences.

@@

\begin{tabular}{|c|c|c|}
	\hline 
	\textbf{Project area}	& \textbf{Noah Peters} 	& \textbf{Nicolas Goeller} 	\\ 
	\hline 
	Data wrangling			&  		   				&  				 			\\ 
	\hline 
	Variable preparation 	&  		   				&  				 			\\ 
	\hline 
	Geodata					&  		   X			&  				 			\\ 
	\hline 
	Git	     			 	&  		   				&  				X 			\\ 
	\hline 			
	Indices				 	&  		   X			&  				 			\\ 
	\hline 
	Paper visualisations 	&  		   				&  				 			\\ 
	\hline 
	Shiny 				 	&  		   				&  				X 			\\ 
	\hline 
	Codebook 			 	&  		   				&  				X 			\\ 
	\hline 
	Geoplots 			 	&  		   X			&  				 			\\ 
	\hline 
	LaTex				 	&  		   				&  				 			\\ 
	\hline 
	Motivation			 	&  		   				&  				X 			\\ 
	\hline 
	Theory				 	&  		   X			&  				 			\\ 
	\hline 
	User manual			 	&  		   				&  				 			\\ 
	\hline 
\end{tabular}

@@

	\newpage
	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	\textbf{Declaration of Authorship}
	\\

	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	We hereby declare that the project paper and all related project elements submitted by the title 
	\\

	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	\textbf{Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors} 
	\\

	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	Are written unaided by ourselves as indicated in the section 'Responsibility for Project Areas'. 
	\\

	\hangindent=\parindent
	\parindent 0pt
	\hangafter=-1
	All indirect or direct sources are acknowledged in the bibliography. We are aware that a false declaration is punishable by law. 
	\\
	\\
	\\
	Place, date                                         	Signature Noah Peters
	\\
	\\
	\\
	\\
	\\
	Place, date												Signature Nicolas Goeller
